Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-26 06_Publication_wireframe_and_7_Questions.Rmd
spell check

# Manuscript wireframe

@@

## Introduction
Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east asia where it is an affordable source of protein [@PulseAustralia]. 
The bean pod or grain can be consumed raw or added to meals after sprouting. 
The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].

Mungbean is grown as a short season summer legume crop which can provide a high returns for growers in eastern Australia. 
A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potenitial crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
Fortunatley a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.

@@

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used soley as a management strategy for mitigating yield losses.
Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].

@@

### Fungicide resistance
Lucritive returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.

>>>>

# Manuscript wire frame

@@

## Introduction
Mungbean [*Vigna radiata* (L.) Wilczek] is a pulse crop primarily grown for human consumption in south-east Asia where it is an affordable source of protein [@PulseAustralia]. 
The bean pod or grain can be consumed raw or added to meals after sprouting. 
The dried grain can also be ground into a protein enriched flour for uses such as noodles, biscuits and cakes [@Chankaew2013].

Mungbean is grown as a short season summer legume crop which can provide a high returns for growers in eastern Australia. 
A crop potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
Fortunately a number of strategies are able to be employed to reduce the damage powdery mildew inflicts on yields.

@@

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used solely as a management strategy for mitigating yield losses.
Quantitative disease resistance has been observed in breeding lines [@Pandey2018; @Chankaew2013] and mungbean cultivars such as Jade-AU, however other management strategies, such as fungicides, are still required[@Kelly2017a].

@@

### Fungicide resistance
Lucrative returns of \$ 2260 over a short three month season may tempt growers into applying fungicide to control diseases such as powdery mildew more than they are needed.
